---
title: "Field Baker's day at campus"
author: "Brandon Medina"
date: "5/02/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(TSP)
```

Young Field Baker is planning his trip to CSUB campus.  He must make 5 stops and one visit to a restroom.  He starts and ends the day at the bus stop on campus

The stops he must make and the North, East coordinates of each are givnen in the following table: (units are Cubits)

   Location     |  coordinates (N, W)
   -------------|--------------------
   Bus stop     |  25, 200
   Engineering Complex |  110, 160
   Dorthy Donahue Building  |  250, 200
   Student Union  |  250, 300
   Walter Stern Library  | 300, 250
   Administration Building | 260  , 50
   
   In addition he must one stop at a  restroom; the available restrooms are at locations (200,160), (340,110), and (280,290)
   
   Find the shortest route freshman Field can take on this visit.  Only 1 restroom stop
   
   
```{r}
y = c(25,110,250,250,300,260,280)
x = c(200,160,200,300,250,50,290)
rrx = c(160,110,290)
rry = c(200,340,280)

```

   
```{r}
tourMAT = ETSP(data.frame(x, y))
tourSolve = solve_TSP(tourMAT)
tour_length(tourSolve)
plot(tourMAT, tourSolve )
points(rrx,rry,col='red',pch=19)
grid()
print(tourSolve)
```
   
Answer 

When Field visits the campus the shortest route for him to take to visit all his stops as well as one bathromm is 823.56 cubits. His route would start at the bust stop, then to Engineering Complex, Administration building, Dorothy Donahue, Walter Stern, bathroom at 280,290, and finally to the student union, before returning to the bus stop.    
   
   